\begin{enumerate}
\item Let $N$ be the set of natural numbers. Suppose $f : N \rightarrow N$ is a function satisfying the following conditions:
    \begin{enumerate}
	    \item $f\brak{mn} = f\brak{m} f\brak{n}$,
	    \item $f\brak{m} < f\brak{n}$ if $m < n$,
	    \item $f\brak{2} = 2$.
    \end{enumerate}
	What is the value of $\sum_{k=1}^{20} f\brak{k}$ ?\hfill(PRERMO 2012)
	\item One is given a finite set of points in the plane, each point having integer coordinates. Is it always possible to color some of the points in the set red and the remaining points white in such a way that for any straight line $L$ parallel to either one of the coordinate axes the difference (in absolute value) between the numbers of white point and red points on $L$ is not greater than $1$?\hfill(IMO 1986)
\item Let $n$ be an integer greater than or equal to $2$. Prove that if $k^2+k+n$ is prime for all integers $k$ such that $0\leq k\leq \sqrt{n/3}$, then $k^2+k+n$ is prime for all integers $k$ such that $0\leq k\leq n-2$ \hfill(IMO 1987)
	\item A function $f$ is defined on the positive integers by
                  \begin{align*}
  f\brak{1}=1, f\brak{3}=3, \\
  f\brak{2n}=f\brak{n}, \\
                  f\brak{4n+1}=2f\brak{2n+1}-f\brak{n},\\
                  f\brak{4n+3}=3f\brak{2n+1}-2f\brak{n},\\ \end{align*}
                  for all positive integers n.
                  Determine the number of positive integers $n$, less than or equal to $1988$,for which $f(n) = n$.\hfill(IMO 1988)
                  \item Show that set of real numbers x which satisfy the in equality                                                                \begin{align*}\sum{k=1}^{70}\frac{k}{x-k}\geq \frac{5}{4}\\ \end{align*}                                                          is a union of disjoint intervals, the sum of whose lengths is $1988$\hfill(IMO 1988)
\item Let $Q^+$ be the set of positive rational numbers. Construct a function $ f: Q^+ \rightarrow Q^+$ such that 

			\begin{align*}  f\brak{xf\brak{y}}= \frac{f\brak{x}}{y} \end{align*}\\ for all $x , y$ in $Q^+$.\hfill(IMO 1990)


      \subsection*{COMBINATOMICS}

  \item Let $S = \{1,2,3,......,280\}$. Find the smallest integer $n$ such that each $n-$ element subset of $S$ contains five numbers which are pairwise relatively prime.\hfill(IMO 1991)

	  \subsection*{GRAPH THEORY}

  \item Suppose $G$ is a connected graph with $k$ edges. Prove that it is possible to label the edges $1,2.....k$ in such a way that at each vertex which belongs to two or more edges, the greatest common divisor of the integers labeling those edges is equal to $1$.
	  $[$ A graph consists of a set of points, called vertices, together with a set of edges joining certain pairs of distinct vertices. Each pair of vertices. $u, v$ belongs to at most one edge. The graph $G$ is connected if for cach pair of distinct vertices $x, y$ there is some sequence of vertices   $x=v_0,v_1,v_2,.......,v_m = y$  such that each pair $v_i,v_{i+1}\brak{0\leq i < m}$ is joined by an edge of G$.]$ \hfill(IMO 1991)
	  \item Let $Q^+$ be the set of positive rational numbers. Construct a function $ f: Q^+ \rightarrow Q^+$ such that 

			\begin{align*}  f\brak{xf\brak{y}}= \frac{f\brak{x}}{y} \end{align*}\\ for all $x , y$ in $Q^+$.\hfill(IMO 1990)
			\item Determine all functions $f: \textbf{R} \to \textbf{R}$ such that\\$f\brak{x - f\brak{y}} = f\brak{f\brak{y}} + xf\brak{y} + f\brak{x} - 1$ \\for all real numbers x,y.\hfill(IMO 1999)
			\item Determine all functions $f:R \rightarrow R $ such that the euality
				\begin{align}
					f(\lfloor{x} \rfloor{y})=f(x) \lfloor{f(y)} \rfloor
				\end{align}
				holds for all $x,y \in R $.(Here $\lfloor{z}\rfloor$ denotes the greatest integer less than or equal to $z$.)\hfill(IMO2010)
			\item Let $f:R \rightarrow R$ be a real-valued function defined on the set of real numbers that satisfies
				\begin{align}
					f\brak x+y \leq{y f\brak x}+f\brak{f\brak x}
				\end{align}
				for all real numbers $x$ and $y$. Prove that $f \brak x=0$ for all $x\leq{0}$.\hfill(IMO2011)
			\item Let $n>0$ be an integer. We are given a balance and $n$ weights of weight $2^{0}, 2^{1}, \dots, 2^{n-1}$. We are to place each of the $n$ weights on the balance, one after another, in such way that the right pan is never heavier than the left pan. At each step we choose one of the weights that has not yet been placed on the balance, and place it on either the left pan or the right pan, unwtil all of the weights have been placed.
				Determine the number of ways in which this can be done.\hfill(IMO2011)
			\item The liar's guessing game is a game played between two players $A$ and $B$. The rules of the game depend on two positive integers $k$ and $n$ which are known to both players. At the start of the game$A$ chooses integers $x$ and $N$ with $1\leq{x}\leq{N}$. Player $A$ keeps $x$ secret, and truthfully tells $N$ to player $B$. Player $B$ now tries to obtain information about $x$ by asking player $A$ questions as follows: each question consists of $B$ specifying an arbitrary set $S$ of positive integers (possibly one specified in some previous question), and asking $A$ whether $x$ belongs to $S$. Player $B$ may ask as many such questions as he wishes. After each question, player $A$ must immediately answer it with yes or no, but is allowed to lie as many times as she wants; the only restriction is that, among any $k + 1$ consecutive answers, at least one answer must be truthful.
				After $B$ has asked as many questions as he wants, he must specify a set $X$ of at most $n$ positive integers. If $x$ belongs to $X$, then $B$ wins; otherwise, he loses. Prove that:
				1. If $n\geq{2^{k}}$, then $B$ can guarantee a win.
				2. For all sufficiently large $k$, there exists an integer $n\geq{1.99^{k}}$ such that $B$ cannot guarantee a win.\hfill(IMO2012)
			\item  Find all positive integers $n$ for which there exist non-negative integers $a_{1}, a_{2}, \dots, a_{n}$ such that
				\begin{align}
					\frac{1}{2^{a_{1}}}+\frac{1}{2^{a_{2}}}+ \dots +\frac{1}{2^{a_{n}}}=\frac{1}{3^{a_{1}}}+\frac{1}{3^{a_{2}}}+ \dots +\frac{n}{3^{a_{n}}}=1.\hfill(IMO2012)
				\end{align}

				\textbf{geometry}
			\item Let $I$ be the incentre of triangle $ABC$ and let $\Gamma$ be its circumcircle. Let the line $AI$ intersect $\Gamma$ again at $D$. Let $E$ be a point on the arc $\overline{BDC}$ and $F$ a point on the side $BC$ such that
				\begin{align}
					\angle{BAF} = \angle{CAE}\angle\frac{1}{2}\angle{BAC}.
				\end{align}
				Finally, let $G$ be the midpoint of the segment $IF$. Prove that the lines $DG$ and $EI$ intersect on $\Gamma$.\hfill(IMO2010)
			\item Let $P$ be a point inside the triangle $ABC$. The lines $AP$, $BP$ and $CP$ intersect the circumcircle $\Gamma$ of triangle $ABC$ again at the points $K,L$ and $M$ respectively. The tangent to $\Gamma$ at $C$ intersects the line $AB$ at $S$. Suppose that $SC=SP$. Prove that $MK=ML$.\hfill(IMO2010)
			\item Let $S$ be a finite set of at least two points in the plane. Assume that no three points of $S$ are collinear. A windmill is a process that starts with a line $l$ going through a single point $P \in S$. The line rotates clockwise about the pivot $P$ until the first time that the line meets some other point belonging to $S$. This point, $Q$, takes over as the new pivot, and the line now rotates clockwise about $Q$, until it next meets a point of $S$. This process continues indefinitely.
				Show that we can choose a point $P$ in $S$ and a line $l$ going through $P$ such that the resulting windmill uses each point of $S$ as a pivot infinitely many times.\hfill(IMO2011)
			\item Let $ABC$ be an acute triangle with circumcircle $\Gamma$. Let $l$ be a tangent line to $\Gamma$, and let $l_{a}, l_{b}, l_{c}$ be the lines obtained by reflecting $l$ in the lines $BC, CA$ and $AB$, respectively. Show that the circumcircle of the triangle determined by the lines $l_{a}, l_{b}, l_{c}$ is tangent to the circle $\Gamma$.\hfill(IMO2011)
			\item Given triangle $ABC$ the point $J$ is the centre of the excircle opposite the vertex $A$. This excircle is tangent to the side $BC$ at $M$, and to the lines $AB$ and $AC$ at $K$ and $L$, respectively. The lines $LM$ and $BJ$ meet at $F$, and the lines $KM$ and $CJ$ meet at $G$. Let $S$ be the point of intersection of the lines $AF$ and $BC$, and let $T$ be the point of intersection of the lines $AG$ and $BC$. Prove that $M$ is the midpoint of $ST$.
				(The $excircle$ of $ABC$ opposite the vertex $A$ is the circle that is tangent to the line segment $BC$, to the ray $AB$ beyond $B$, and to the ray $AC$ beyond $C$.)\hfill(IMO2012)
			\item  Let $ABC$ be a triangle with $\angle{BCA}=90^{\circ}$, and let $D$ be the foot of the altitude from $C$. Let $X$ be a point in the interior of the segment $CD$. Let $K$ be the point on the segment $AX$ such that $BK = BC$. Similarly, let $L$ be the point on the segment $BX$ such that $AL=AC$. Let $M$ be the point of intersection of $AL$ and $BK$.
				Show that $MK=ML$.\hfill(IMO2012)
				\item Let $R$ be the set of real numbers. Determine all functions $f:R\rightarrow R$ such that, for all real numbers $z$ and $y$, \begin{align}f(f(x)f(y))+f(x+y)=f(xy)\end{align}.\hfill (IMO 2017)
				\item Let ${R}$ denote the set of all real numbers. Find all functions $f : {R}$ $\rightarrow$ ${R}$ such that                                           

$f(x^{2}+f(y))=y+(f(x))^{2}$                          
                                       
for all $x, y$ $\epsilon$ $R$.  \hfill(IMO 1992)
\item Does there exist a function $f : N \rightarrow N$ such that $f(1) = 2$, $f(f(n)) = f(n) + n$ for all $n$ $\epsilon$ $N$, and $f(n) < f(n + 1)$ for all $n$ $\epsilon$ $N$ ? \hfill(IMO 1993)
\item Let $S$ be the set of real numbers strictly greater than $-1$. Find all functions $f : S \rightarrow S$  satisfying the two conditions:                                                                 
	$1$. $f(x + f(y) + xf(y)) = y + f(x) + yf(x)$ for a  $x$ and $y$ in $S$;                                                                                                           
$2$. $\frac{f(x)}{x}$ is strictly increasing on each of the intervals $-1<x<0$                                                    
		 and $0<x$.   \hfill(IMO 1994)
\end{enumerate}
